Nature Neuroscience Submission Letter

### 2019-09-06 paper/nature neuroscience submission/cover_letter.tex
added emails to cover letter

  We have suggested the following scientists as expert reviewers:
  Richard Betzel (EMAIL), Danielle Bassett (EMAIL), Emily Finn
  (EMAIL), Olaf Sporns (EMAIL), and Christopher Honey (EMAIL).

>>>>

  We have suggested the following scientists as expert reviewers:
  Richard Betzel (rbetzel@indiana.edu), Danielle Bassett (dsb@seas.upenn.edu), Emily Finn
  (emily.finn@nih.gov), Olaf Sporns (osporns@indiana.edu), and Christopher Honey (chris.honey@jhu.edu).
